Blame and Coercion: Together Again for the Second Time

### 2019-10-18 paper.tex
intro editing

Around 2006, several groups of researchers proposed ways to integrate
dynamic typing and static typing, notably gradual typing
\citep{siek2006gradual}, hybrid typing \citep{flanagan2006hybrid},
migratory typing \citep{Tobin-Hochstadt:2006fk}, and multi-language
iteroperability \citep{Gray:2005ij,Matthews:2007zr}. Researchers
usually define the semantics of gradually typed languages by
translation to an intermediate language with casts, such as the blame
calculus \citep{wadler2009well} and other cast calculi
\citep{siek2009exploring}. Unfortunately, straightforward
implementations of casts on higher-order values (functions, objects,
etc.) impose significant runtime overheads that can change the
asymptotic time and space complexity of a program
\citep{herman2010space}. There are several known space-efficient cast
representations, with various strengths and weaknesses. This paper
presents a new cast representation, named \emph{hypercoercions}, that
is good for both mechanized metatheory and good for implementation.
The composition operator for hypercoercions is structurally recursive
and the hypercoercions are suggestive of a bit-level representation
that minimizes the need for pointers and fits all first-order casts
into 64 bits.  Of course, valid cast representation must not change
the result of programs. This paper presents first steps toward a
framework for proving the equivalence of cast calculi.

>>>>

Around 2006, several groups of researchers proposed ways to integrate
dynamic typing and static typing, notably gradual typing
\citep{siek2006gradual}, hybrid typing \citep{flanagan2006hybrid},
migratory typing \citep{Tobin-Hochstadt:2006fk}, and multi-language
iteroperability \citep{Gray:2005ij,Matthews:2007zr}. Researchers
usually define the semantics of gradually typed languages by
translation to an intermediate language with casts, such as the blame
calculus \citep{wadler2009well} and other cast calculi
\citep{siek2009exploring}. Unfortunately, straightforward
implementations of casts on higher-order values (functions, objects,
etc.) impose significant runtime overheads that can change the
asymptotic time and space complexity of a program
\citep{herman2010space}. There are several known space-efficient cast
representations, with various strengths and weaknesses \citep{siek2015blame,siek2010threesomes,garcia2013calculating,kuhlenschmidt2018efficient,siek2012interpretations,Garcia-Perez:2014aa}. This paper
presents a new cast representation, named \emph{hypercoercions}, that
is good for both mechanized metatheory and good for implementation.
The composition operator for hypercoercions is structurally recursive
and the hypercoercions are suggestive of a bit-level representation
that minimizes the need for pointers and fits all first-order casts
into 64 bits.  Of course, valid cast representation must not change
the result of programs. This paper presents first steps toward a
framework for proving the equivalence of cast calculi.
